% Awesome Source CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/awesome-neue-latex-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Professional experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}

  \experience
  {Current} {Devops Engineer (cloud)| C2IMERA, Leidos Inc.}{Beavercreek}{Ohio}
  {June 2021} {
      \begin{itemize}
          \item Successfully managed multiple responsibilities as the sole DevOps Engineer on the team, effectively collaborating with cross-functional teams to meet project goals.
          \item Implemented an api gateway rollout strategy, enabling streamlined and secure communication between various microservices.
          \item Migrated over 1200 locally run tests onto AWS, reducing build times by over two hours and significantly improving software development efficiency.
          \item Proactively collaborated with security teams to implement and maintain best practices for securing cloud-based infrastructure and applications, including multi-factor authentication and encryption protocols.
          \item Partnered closely with development teams to implement automated testing and continuous integration processes, ensuring high-quality and consistent software releases.
          \item Designed and executed a Kafka-based infrastructure to successfully migrate a monolithic application into a microservice-based architecture, resulting in improved scalability, reliability, and agility.
          \item Designed and implemented an end-to-end build and deployment strategy for Git branches that can be executed with a single command, significantly reducing deployment time and effort.
      \end{itemize}
  }
  {Java, AWS, Terraform, Kafka, Kong, CI/CD, Gradle}
  \emptySeparator
  \experience
  {May 2021} {DevOps Engineer | AIMES, Leidos Inc.}{Beavercreek}{Ohio}
  {January 2019} {
      \begin{itemize}
          \item Setup and managed a private PKI signing service that improved security and reduced dependencies on third-party services.
          \item Designed and established a centralized repository structure using Artifactory and Nexus that enabled the efficient archiving of artifacts and deployments, leading to faster development cycles and smoother operations.
          \item Created and maintained fully automated CI/CD pipelines for code deployment using Docker, Jenkins, AWS, and Vsphere, ensuring optimal integration of the pipelines with the software development lifecycle.
          \item Collaborated closely with Software Engineers, Product Managers, and QA Engineers in an Agile team environment to ensure optimal integration of the pipelines with the software development lifecycle.
      \end{itemize}
  }
  {Python, AWS, Atlassian, CI/CD, Git, Jenkins}
  \emptySeparator
  \experience
    {December 2019}   {DevOps Engineer | Insite, Crown Equipment}{New Breman}{Ohio}
    {January 2018} {
      \begin{itemize}

          \item Designed and implemented fully automated CI/CD pipelines for code deployment using Docker, Bamboo, and AWS, resulting in significant time savings and increased efficiency for the development team.
          \item Maintained and managed over 2000 active pipeline builds for code written in multiple programming languages, including Java, Nodejs, Python, C++, C\#, and Matlab, ensuring smooth and seamless code deployment.
          \item Developed Python and Shell scripts to optimize the utilization of AWS resources, increasing the performance, reliability, and ease of use of the cloud infrastructure.
          \item Created and managed Cloudformation templates for deploying AWS cloud infrastructures as code, simplifying the process of deploying and maintaining cloud infrastructure.
          \item Successfully led bi-weekly releases of a micro-service based application to an average of 150 AWS instances, ensuring smooth and timely software releases.
          \item Implemented secure user practices and principles to conform with ISO/IEC 27001, ensuring the highest level of security for the cloud infrastructure and applications.
      \end{itemize}
  }
  {Python, AWS, Cloudformation, Atlassian, CI/CD, Git}
  \emptySeparator
  \experience
    {September 2017}   {Graduate Research Assistant | Web and Complex Systems Lab, Wright State University}{Dayton}{Ohio}
    {September 2014} {
      \begin{itemize}

          \item Collaborated with a team of developers to create a multi-language software platform for data analysis
          \item Published research paper titled \textit{WAMINet : An Open Source Library for Dynamic Geospace Analysis Using WAMI} showcasing software development skills and research accomplishments
          \item Co-founded the Web and Complex Systems Laboratory to promote interdisciplinary research and development
          \item Coordinated with research advisors and team members to ensure software met project requirements and timelines
      \end{itemize}
  }
  {Java, R, Python, HTML, Javascript, Maven, Git}
  \emptySeparator
  \experience
  {August 2014} {Asst. Systems Administrator | Kno.e.sis Research Center, Wright State University}{Dayton}{Ohio}
  {January 2014} {
      \begin{itemize}
          \item Successfully fulfilled various technical roles as the sole support member for Kno.e.sis Research Center, ensuring that all technical issues were promptly resolved
          \item Maintained email, project, and web servers to ensure optimal performance and minimize downtime
          \item Created and maintained an Openstack virtualization cluster containing over 70 nodes, which increased computing capacity and efficiency for research activities
          \item Conducted regular system backups, monitored system logs, and implemented security protocols to ensure the safety and integrity of all data and systems
      \end{itemize}
  }
  {Linux, Openstack, Windows Server, Networking, Technical Support}
  \emptySeparator
  \experience
  {December 2014} { Asst. Systems Administrator | Department of Computer Science, Wright State University }{Dayton}{Ohio}
  {April 2012}    {
      \begin{itemize}
          \item Maintained lab computers by installing operating systems and security patches to ensure optimal performance and security.
          \item Installed and cataloged lab equipment, including building custom computers for staff and faculty, to ensure that equipment is up to date and functioning correctly.
          \item Assisted System Administrator with daily tasks such as network and server maintenance, ensuring smooth and efficient operations.
          \item Utilized Windows and Linux operating systems and Acronis backup software to maintain system backups and ensure data recovery in case of system failure.
      \end{itemize}
  }
  {Windows,Linux,Acronis}
  \emptySeparator
  \experience
    {December 2014}     { Programming Tutor | Department of Computer Science, Wright State University }{Dayton}{Ohio}
    {April 2012}    {
      \begin{itemize}
        \item Instructed students in Java Programming assignments, providing guidance and feedback on programming concepts and assignments to help them achieve their academic goals.
        \item Conducted one-on-one and group tutoring sessions, tailored to meet the needs of individual students, and provided guidance on a wide range of topics including object-oriented programming, algorithms, and data structures.
        \item Maintained a positive and supportive learning environment, promoting engagement and learning among students with diverse backgrounds and skill levels.
      \end{itemize}
    }
    {JAVA, C++}
  \emptySeparator
%  \experience
%  {December 2011}     { Web Development Intern | Edict Systems }{Dayton}{Ohio}
%  {January 2011}    {
%      \begin{itemize}
%          \item Programmed business translations for Electronic Data Interchange (EDI) financial transactions, utilizing my knowledge of XML and its manipulation using XSLT and XQuery.
%          \item Designed and created a standardized set of XSLT datatype filters for data validation, which improved the accuracy and efficiency of data processing.
%          \item Collaborated with cross-functional teams of developers, quality assurance testers, and project managers to ensure timely and successful completion of various projects.
%          \item Demonstrated strong communication skills, both written and verbal, in collaborating with team members and presenting work to customers.
%      \end{itemize}
%  }
%  {HTML, JavaScript, XML, XSLT, XQuery}
%  \emptySeparator
%  \experience
%  {December 2010} { Physics Tutor | Sinclair Community College }{Dayton}{Ohio}
%  {August 2010}{
%      \begin{itemize}
%          \item Provided individual and group tutoring sessions to undergraduate students enrolled in the sinclair physics courses
%          \item Conducted preparation and review sessions prior to exams, covering key concepts and problem-solving strategies to help students prepare and succeed
%          \item Collaborated with faculty members to identify areas where students commonly struggle and develop techneques to address their challenges
%      \end{itemize}
%  }
%  {}


\end{experiences}
